% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca (fork 1)
% (c) 2016 Ananda Seelan <ananda.seelan@gmail.com> (fork 2)
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{lmodern}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\textbf{\sffamily{\mbox{~}{\large #1} \vphantom{p\^{E}}}}}
%{{\large \textbf{#1 \vphantom{p\^{E}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}
%-----------------------------------------------------------
\pagestyle{fancy}
\fancyhead{} % clear all header fields
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{\fontsize{7}{4}\selectfont Sri Ananda Seelan - Resume - forked from the original \LaTeX \ template by Matthew Boedicker and David J. Grant}
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Sri Ananda Seelan}  & 91 9789269542\\
Chengalpet &  ananda.seelan@gmail.com \\
\end{tabular*}
\\
\vspace{0.05in}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\vspace{0.025in}

\resheading{Education}
\begin{itemize}
\item[]
	\ressubheading{Amrita School of Engineering, Amrita Vishwa Vidyapeetham}{Coimbatore, India}{Bachelor of Technology, Computer Science and Engineering (CGPA: 8.29)}{2010 - 2014}

\item[]
	\ressubheading{Sri Sarada Balamandir Boys' Matric Hr. Sec. School}{Salem, India}{TamilNadu Higher Seconday School Examination (Score: 95\%)}{2010}

\end{itemize}

\resheading{Programming Skills}
\vspace{-2mm}
\begin{itemize}
\item[]{\textit{Languages:} C, C++, Python-2.X, Java, JavaScript, HTML, Dart(under study), Scheme(under study)}\vspace{-2mm}
\item[]{\textit{Databases:} MySQL}\vspace{-2mm}
\item[]{\textit{GUI Toolkits:} wxWidgets}\vspace{-2mm}
\item[]{\textit{Web Development Frameworks:} Python Flask, jQuery, Twitter Bootstrap, Enyo JS}\vspace{-2mm}
\item[]{\textit{Operating Systems:} Linux (mainly Ubuntu, OpenSuse but also familiar with other distributions)}\vspace{-2mm}
\item[]{\textit{Version Control Systems:} Mercurial}\vspace{-2mm}
\end{itemize}

\vspace{0.05in}
\resheading{Interests}
\vspace{-2mm}
\begin{itemize}[leftmargin=.5in]
\item{General purpose programming}\vspace{-3mm}
\item{Web development}\vspace{-3mm}
\item{RESTful API}\vspace{-3mm}
\item{Information Systems}\vspace{-3mm}
\end{itemize}

\vspace{0.05in}
\resheading{Work Experience}
\begin{itemize}
\item[]
	\ressubheading{Zoho Corporation}{Chennai, India}{Member Technician Staff, ManageEngine ServiceDesk Plus OnDemand}{April 2014 - Present}
	\begin{itemize}
		\resitem{Part of a team working on developing a RESTful web framework that is typically used everyday by module/feature developers for quickly implementing REST APIs.}
		\resitem{\textit{The framework is being written with core Java. Responsibilities include active development and maintenance of core parts of this framework.}}
	\end{itemize}

\item[]
	\ressubheading{Zoho Corporation}{Chennai, India}{Project Intern, ManageEngine ServiceDesk Plus OnDemand}{Feb 2014 - March 2014}
	\begin{itemize}
		\resitem{Developed a Computer Telephony Integration addon for ServiceDesk Plus OnDemand - a cloud based IT Help Desk software.}
		\resitem{\textit{Wrote API bindings and a standalone client application for Avaya PBX.}}
	\end{itemize}

\item[]
	\ressubheading{Human Factors International}{Pondicherry, India}{Intern}{Dec 2012}
	\begin{itemize}
		\resitem{Interned with a contractor for HFI working on a cross-platform desktop application to monitor their servers. This application serves as a control panel that is being used by the employees to control and monitor their remote servers.}
        \resitem{\textit{Primarily worked with adding/tweaking few GUI components of this application written with wxWidgets.}}
	\end{itemize}

\item[]
	\ressubheading{Amrita Multi-dimensional Data Analytics Research Lab}{Coimbatore, India}{Undergraduate Student Researcher}{May 2012 - Dec 2013}
	\begin{itemize}
		\resitem{Was part of a team of research interns who were working on several Information Retrieval projects in Amrita MultiDimensional Data Analytics Lab, Department of CSE.}
	\end{itemize}

\end{itemize}

\resheading{Projects}
\begin{itemize}
\item[]
	\textbf{A statistical approach for modeling Inter-Document relatedness}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{This work, done at the Amrita Multi dimensional Data Analytics Lab was aimed at devising a statistical model that automatically identifies and quantifies different types of relatedness between scientific/technical documents. This system would find important applications in educational Digital libraries to help a user by directing the order of material he/she searches to learn.}
		\resitem{Consequently, a research article was written by us with the above title and the manuscript has been communicated with \textit{"Journal of Intelligent Information Systems"} - a reputed research journal.}
	\end{itemize}

\item[]
	\textbf{Incremental and Hierarchial index for faster TF-IDF calculation}
	\vspace{-3mm}
	\begin{itemize}
	    \resitem{This project was aimed at reducing the calculation time of TF-IDF, an important and fundamntal metric in Searching and Ranking.}
		\resitem{Designed and implemented an incremental and hierarchial index with an in-memory key value store and achieved faster calculation of this metric.}
		\resitem{\textit{This utility was written in Python.}}
	\end{itemize}

\item[]
	\textbf{Feedback aggregation tools for a Video Recommender system}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{Developed a couple of simple video browsing applications along with a recommender system based on the results of our previous project "A statistical approach for modeling Inter-document relatedness". These web applications were used to log user feedback(both implicit as well as explicit) and check the user intent against our results.}
		\resitem{\textit{Python was the primary language on which the servers were written with Flask as the web framework. SQLite was used as the database server and jQuery for frontend.}}
	\end{itemize}

\item[]
	\textbf{Docu}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{Docu is a desktop application that features a text editor written over Google Closure editor, to support text editing in a number of Indian languages including Hindi, Bengali, etc.}
		\resitem{\textit{This being primarily a JavaScript application, was bundled as a desktop application using node-webkit aka nw.js for webkit bindings.}}
	\end{itemize}

\item[]
	\textbf{Collision Course}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{A 2D ball dodging game written during a 24 hour code-a-thon which also won the third place in the same event.}
		\resitem{\textit{The game ran on HTML canvas using the box2D JavaScript engine.}}
	\end{itemize}

\item[]
	\textbf{Monopoly}
	\vspace{-3mm}
	\begin{itemize}
		\resitem{A desktop version of the classic Monopoly board game.}
		\resitem{\textit{Was written in C++ with WIN32 graphics library support.}}
	\end{itemize}

\end{itemize}

\resheading{Achievements}
\vspace{-3mm}
	\begin{itemize}
		\item Qualified for the ACM-ICPC 2014, Amritapuri regionals
		\vspace{-3mm}
		\item Won the third place in a web-designing event held during a National level Student Convention conducted by Computer Society of India
		\vspace{-3mm}
		\item Secured the third position in a code-a-thon event conducted by Amrita School of Engineering-Bangalore for developing a game application in 24 hours
		\vspace{-3mm}
		\item Won the second place in "Hexathalon", a technical event conducted during a National level Tech. Fest conducted by Amrita University
    \end{itemize}
    
\vspace{2cm}
(Last updated on 17/5/2016)

\end{document}